The unequal distribution of access to education and transport: insights from the São Paulo Metropolitan Region

### 2017-04-02 paper_v2.tex
Improve text

For this work we used the Google Matrix Distance API
(API stands for `application programming interface' and is used for
computer-computer communication over the web), a multi-modal
real-time travel data provider (see \url{https://developers.google.com/maps/documentation/distance-matrix/}). 
The API was used in preference to other options,
such as Routino, described in a paper by Singleton (2014),
and the OpenStreetMap Routing Machine (OSRM)
because its
ease of use (requiring no new software to be installed locally)
and performance: the Google Distance Matrix
API returns
route distance, price and times for journeys between origins and
destinations, provided either as Longitude/Latitude pairs or
as text strings to be 'geocoded' (converted to geographical location).

>>>>

For this work we used the Google Matrix Distance API
(application programming interface), a multi-modal
real-time travel data provider (see \href{https://developers.google.com/maps/documentation/distance-matrix/}{developers.google.com/maps/}). 
The API was used in preference to other options,
such as Routino --- see Singleton (2014) for a used case involving large-scale accessibility analysis ---
and the OpenStreetMap Routing Machine (OSRM)
because its
ease of use (requiring no new software to be installed locally)
and performance: the Google Distance Matrix
API returns
route distance, price and times for journeys between origins and
destinations, provided either as Longitude/Latitude pairs or
as text strings to be 'geocoded' (converted to geographical location).
